Timeliness of security updates for Android

### 2014-11-12 securityupdates.tex
Re-run versions.py with updated latex_value

%An analysis by Vidas et al.~\cite{Vidas2011} of the Android 2.1 to 2.2 update found that it took 11 months from when Google released 2.2 for the last device which they were investigating to get the update.
To compute the latency between upstream releases and their inclusion in Android we scraped the release pages for those projects, to obtain the version numbers and release dates.
This allows us to compute the latency between an upstream project being released and it being included in Android, this is shown in Table~\ref{tab:update_ecosystem}.
The versions included in Android were about half a year old when the first version of Android containing it was released.
\begin{table}
\centering
\normalsize
\begin{tabular}{l|r|r}
Project	&	\# releases	&	latency \\ \hline
linux	&	\linuxNumVersions	&	\linuxMeanUpdateLatency \\
openssl	&	\opensslNumVersions	&	\opensslMeanUpdateLatency \\
bouncycastle	&	\bouncycastleNumVersions	&	\bouncycastleMeanUpdateLatency \\
\end{tabular}
\caption{Flow of updates from upstream projects into Android. Number of updates as in Figure~\ref{fig:update_ecosystem}, latency in days for all pairs of versions we have data on.\todolater{scrape the other 26 websites... is it worth it?}}
\label{tab:update_ecosystem}
\end{table}

>>>>

%An analysis by Vidas et al.~\cite{Vidas2011} of the Android 2.1 to 2.2 update found that it took 11 months from when Google released 2.2 for the last device which they were investigating to get the update.
To compute the latency between upstream releases and their inclusion in Android we scraped the release pages for those projects, to obtain the version numbers and release dates.
This allows us to compute the latency between an upstream project being released and it being included in Android, this is shown in Table~\ref{tab:update_ecosystem}.
The versions included in Android were about half a year old when the first version of Android containing it was released.
\begin{table}
\centering
\normalsize
\begin{tabular}{l|r|r}
Project	&	\# releases	&	latency (days) \\ \hline
linux	&	\linuxNumVersions	&	\linuxMeanUpdateLatency \\
openssl	&	\opensslNumVersions	&	\opensslMeanUpdateLatency \\
bouncycastle	&	\bouncycastleNumVersions	&	\bouncycastleMeanUpdateLatency \\
\end{tabular}
\caption{Flow of updates from upstream projects into Android. Number of updates as in Figure~\ref{fig:update_ecosystem}, latency in days for all pairs of versions we have data on.\todolater{scrape the other 26 websites... is it worth it?}}
\label{tab:update_ecosystem}
\end{table}
